### 2018-06-19 doc/latex/01-Introduction.tex

We use a $Simulator$ class to organize the activities from the people in the population.
The ContactPools in a population are grouped into ContactCenters (e.g. the different classes of a school are grouped into one K12School ContactCenter}
These ContactCenters are geographically grouped into a geographical grid (sometimes called GeoGrid)

>>>>

We use a $Simulator$ class to organize the activities from the people in the population.
The ContactPools in a population are grouped into ContactCenters (e.g. the different classes of a school are grouped into one K12School ContactCenter).
These ContactCenters are geographically grouped into a geographical grid (sometimes called GeoGrid)
